On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-04 docs/mvfits_paper/mvf.tex
Specifying how training data are computed; ie Leaver

Worst, in cases where the underlying dataset is best described by a rational function, a rational model with maximum monomial degree $K$ will typically outperform a polynomial model of maximum degree $K$ with the same number of coefficients as the rational model.

@@

\eqns{eq:cw_fit_1}{eq:cw_fit_9} display the resulting polynomial models.

@@

\par \fig{fig:ys} displays fits, training data and related residuals.

>>>>

@@

\eqns{eq:cw_fit_1}{eq:cw_fit_9} display the resulting polynomial models to numerical results of Leaver's method~\cite{Leaver85}.

@@

\par \fig{fig:ys} displays fits, training data and related residuals. The training data were compute using Leaver's representation for the spheroidal harmonics to evaluate \eqn{sigma}.
